\documentclass[11pt,a4paper]{article}
\usepackage[margin=1.8cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\setlist{nosep}
\pagenumbering{gobble}
\begin{document}
\begin{center}
{\LARGE Ziqian Guo}\\[4pt]
China Agricultural University \textbullet{} Mechanical Design, Manufacturing and Automation\\
Phone: 13120351856 \textbullet{} Email: \href{mailto:2022714goo@gmail.com}{2022714goo@gmail.com} \textbullet{} GitHub: \href{https://github.com/qianxvde}{qianxvde}
\end{center}

\section*{Focus}
Humanoid robot soccer, fall recovery, reinforcement learning, ROS2 strategy, and deployment.

\section*{Education}
\textbf{China Agricultural University} \hfill Beijing, China\\
B.Eng. in Mechanical Design, Manufacturing and Automation \hfill Sept. 2024 -- Present

\section*{Competition Experience}
\textbf{CAU RoboCup Humanoid Robot Team} \hfill Oct. 2025 -- Present\\
Core member: strategy, ROS2 integration, recovery policy deployment, hardware debugging.\\
Champion: RoboCup China Middle Group; RoboLeague Wuhan; monthly Beijing league. Runner-up: RoboCup World Championship Incheon Large Group.

\section*{Open-source Projects}
\textbf{my\_mjlab} --- Humanoid fall recovery RL (loco\_recovery) on MJLab/MuJoCo.\\
\textbf{my\_hhtools} --- Humanoid motion retargeting and training-data conversion.\\
\textbf{my\_wbc\_fsm} --- Policy deployment FSM with safety checks for humanoid platforms.

\section*{Skills}
Python, basic C++, Linux, Git, MuJoCo, MJLab, RSL-RL, ROS2, motion retargeting.
\end{document}
